Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-12-14 paper/main.tex
Moved optimization results away from results

\subsection{Theoretical optimized results}

Tables \ref{tbl:tahoe:optimized_g} and \ref{tbl:tahoe:optimized_p} exhibit
the results calculated using the best \ac{SUPERCOP} implementation for each
candidate from Section \ref{sec:results:supercop}, the exact sizes for each
call to the hash function from Section \ref{sec:results:tahoedata}, and
interpolation to estimate the time to hash a length not recorded by
\ac{SUPERCOP}. For lengths above 4096B, the numbers for long data lengths are
used. The results also assume only one core of the reference processor is used.

\input{tables/tahoe_optimized_p}
\input{tables/tahoe_optimized_g}

@@

>>>>

@@

\subsection{Theoretical optimized results}
We have not use the fastest available implementations for all of the
candidates, we also know that our bindings creates an overhead for all calls.
Therefore we have tried to calculate the results that could have been achieved
in Tahoe-\ac{LAFS} if we had managed to obtain the speeds of the fastest
implementations in \{SUPERCOP}. The results can be seen in appendix XX.
%TODO: Fik appendix og referanse

%Tables \ref{tbl:tahoe:optimized_g} and \ref{tbl:tahoe:optimized_p} exhibit
%the results calculated using the best \ac{SUPERCOP} implementation for each
%candidate from Section \ref{sec:results:supercop}, the exact sizes for each
%call to the hash function from Section \ref{sec:results:tahoedata}, and
%interpolation to estimate the time to hash a length not recorded by
%\ac{SUPERCOP}. For lengths above 4096B, the numbers for long data lengths are
%used. The results also assume only one core of the reference processor is used.

%\input{tables/tahoe_optimized_p}
%\input{tables/tahoe_optimized_g}
